%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Robotics Engineer} % Job title
    {May Mobility} % Organization
    {Ann Arbor, Michigan} % Location
    {Jun 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Product lead for development and deployment of hardware and software for classification of traffic lights with vehicle camera}
        \item {Developed tools for supporting development and operations team. (camera calibrator, infrastructure monitor, mapping tools, etc.)}
        \item {Shipped production-ready software for vision-based traffic light classification on fixed infrastructure nodes}
        \item {Supported new and existing deployments by providing on-site support for vehicle hardware and software}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student Research Associate} % Job title
    {University of Michigan} % Organization
    {Ann Arbor, Michigan} % Location
    {May 2017 - Apr 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Kinematically-informed Interactive perception \href{https://arxiv.org/abs/1901.05580}{[Link]}, enables robots to classify objects by building 3D models through observations from a RGBD camera while manipulating the object. Method was validated on Toyota’s HSR Robot}
        \item SPARE {\href{https://arxiv.org/abs/1803.11147}{[Link]}, extendable articulated object RGBD dataset, using simulation environment Gazebo. Our method could randomize number of links, their lengths and color and be observed from multiples viewpoints over time. Proposed deep learning architecture (Conv3D/Conv+LSTM, FC) to count links and estimate link lengths(Tensorflow)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
	{Graduate Student Instructor, Mathematics for Robotics} % Job title
	{} % Organization
	{} % Location
	{Sep 2017 - Dec 2017} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Lectured on topics in linear algebra. Set assignments, term exams and held office hours (88 graduate students)}
		\end{cvitems}
	}
%---------------------------------------------------------
  \cventry
	{Graduate Student Instructor, Advanced Topics in Computer Vision} % Job title
	{} % Organization
	{} % Location
	{Jan 2017 - Apr	 2017} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Covered pictorial structures, graphical models, CNN, GAN, RNN, LSTM, auto-encoders, etc. Created weekly in-class problems, and programming assignments and held office hours (class of 75 graduate students)}
		\end{cvitems}
	}      
\vspace{0.4cm}
%---------------------------------------------------------
  \cventry
    {Senior Engineer, Electronics Integration} % Job title
    {Ather Energy Pvt. Ltd.} % Organization
    {Bangalore, India} % Location
    {Jul 2015 - Jul 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Headed a team of 6, responsible for designing electrical (signal and power) interface between all subsystems, waterproof housings for vehicle dashboard and power distribution unit}
        \item {Performed system level DFMEA and incorporated hardware changes to accommodate on-board diagnostics}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
	{Senior Field Engineer, Wireline} % Job title
	{Schlumberger Asia Services Ltd.} % Organization
	{Mumbai, India} % Location
	{Jul 2012 - May 2015} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item{Lead Engineer for ONGC offshore wireline operations; carried out over 80 logging jobs as the engineer in charge}
			\item {Planned and executed many high profile (~\$400K revenue/job) operations in offshore oil rigs, lasting over 150 hours while keeping quality and safety as priority, taking critical decisions while operating with limited connectivity to base}
			\item {Worked in culturally diverse teams with varied nationality, heading teams consisting up to 8 crew members}
		\end{cvitems}
	}

\end{cventries}
